GVN-Hoist: Hoisting Computations from Branches

### 2016-08-08 hoist.tex
calls

@@

\subsubsection{Hoisting calls}
Calls can be hoisted by value-numbering all the arguments. For safety
we have to check that there are no other side-effects between a call and
its hoisting point, just like we did for loads and stores.

>>>>

For legality we have to check that the side-effects of call does not intersect
any side-effect between the instruciton to be hoisted and its hoisting point.

@@

\subsubsection{Hoisting calls}
llvm has built in facility to value-number calls. If there are calls in sibling
branches with identical value numbers, they can be hoisted. For legality we have
to check that the loads/stores in the call does not create hazard with any
loads/stores (in the caller) in the path from callsite through the hoisting
point, just like we did for loads and stores.
